Check Coverage

### 2019-10-07 analysis/merge_data.Rmd
Create standard FD and study tables

check if all bird & mammal biotime data w/id's has an elton match. There are 63 species without a match (54 are birds).
```{r}
no_trait <- biotime_data %>%
  filter(taxa %in% c("Birds", "Mammals")) %>%
  select(id, sourceName, taxa) %>%
  drop_na(id) %>%
  distinct() %>%
  filter(!id %in% elton_bird$id, !id %in% elton_mamm$id)

@@

biotime_traits_list <- map2(taxa, traits, ~merge_data(taxa = .x, trait_data = .y))
coverage <- map_dfr(biotime_traits_list, get_coverage) %>%
  filter(perc > percent)

biotime_traits <- map_dfr(biotime_traits_list, ~drop_na(., scientificName)) %>%
  filter(study_id %in% coverage$study_id)
```

@@

fd <- biotime_traits %>% 
  filter(!is.na(plot)) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  group_by(study_id, plot) %>%
  group_map(~get_fd_safe(.x, study = .y$study_id, plot = .y$plot))
```

Read data back in:
```{r}
files <-  dir(here::here("data", "fd_output"), "*.tsv")

fd_data <- files %>%
  paste0(here::here("data", "fd_output"), "/", .) %>%
  map_dfr(read_tsv)

fd <- biotime_traits %>% 
  filter(!is.na(plot), !study_id %in% c(195, 360)) %>%
  anti_join(fd_data) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  group_by(study_id, plot) %>%
  group_map(~get_fd_safe(.x, study = .y$study_id, plot = .y$plot))

#4610981
#7611121

@@

>>>>

check if all bird & mammal biotime data w/id's has an elton match. There are 68 species without a match (63 are birds).
```{r}
no_trait <- biotime_data %>%
  filter(taxa %in% c("Birds", "Mammals")) %>%
  select(id, sourceName, taxa) %>%
  drop_na(id) %>%
  distinct() %>%
  filter(!id %in% elton_bird$id, !id %in% elton_mamm$id)

@@

biotime_traits_list <- map2(taxa, traits, ~merge_data(taxa = .x, trait_data = .y))

#this gives a coverage for each trait dataset, so potentially a lot of coverage with one dataset and no coverage on all the rest
#need to get rid of zeros when there is coverage from another dataset so we only have one entry per study
coverage <- map_dfr(biotime_traits_list, get_coverage) %>% 
  filter(perc > 0)%>%
  right_join(biotime_data %>% select(study_id) %>% distinct()) %>%
  mutate(perc = replace_na(perc, 0))

inc_coverage <- coverage %>% filter(perc > percent)

biotime_traits <- map_dfr(biotime_traits_list, ~drop_na(., scientificName)) %>%
  filter(study_id %in% inc_coverage$study_id)
```

@@

fd <- biotime_traits %>% 
  filter(!is.na(plot)) %>%
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  filter(study_id == 516) %>%
  group_by(study_id, plot) %>%
  group_map(~get_fd_safe(.x, study = .y$study_id, plot = .y$plot)) %>%
  bind_rows()
```

Read data back in:
```{r}
# files <-  dir(here::here("data", "fd_output"), "*.tsv")
# 
# fd_data <- files %>%
#   paste0(here::here("data", "fd_output"), "/", .) %>%
#   map_dfr(read_tsv)
# 
# fd <- biotime_traits %>% 
#   filter(!is.na(plot), !study_id %in% c(195, 360)) %>%
#   anti_join(fd_data) %>%
#   group_by(study_id, year, plot) %>%
#   filter(n_distinct(id) > 4) %>%
#   ungroup() %>%
#   group_by(study_id, plot) %>%
#   group_map(~get_fd_safe(.x, study = .y$study_id, plot = .y$plot))
# 
# #4610981
# #7611121

@@

Format tables
```{r}
fd_table <- fd %>% 
  select(year, study_id, plot, richness = nbsp, everything(), -sing.sp) %>%
  gather(metric, value, contains("F"), RaoQ) %>%
  View()

study_table <- biotime_data %>%
  group_by(study_id) %>%
  mutate(min_year = min(year), max_year = max(year)) %>% 
  #select(study_id, plot, taxa, latitude, longitude, min_year, max_year) %>%
  select(study_id, taxa, min_year, max_year) %>%
  distinct() %>%
  left_join(coverage, by = "study_id")
```
